From the function-sheaf dictionary to quasicharacters of $p$-adic tori

### 2015-07-22 cover letter.tex
Small fixes to cover letter

We reorganised the Introduction to reflect the changes discussed below. This included making a subsection called {\it Relation to other work}, following a recommendation.

@@

@@

We changed nomenclature so that the paper now discusses two notions: {\it character sheaves} and {\it quasicharacter sheaves}. Character sheaves are based on a familiar concept: they are local systems on a smooth group scheme $G$ over a finite field $k$, equipped with some additional structure, and they provide a geometrization of characters of $G(k)$.  Quasicharacter sheaves provide a geometrization of quasicharacters of $p$-adic tori $T(K)$; they are local systems equipped with some additional structure, on the Greenberg transform of a Neron model. 

@@

In Section 4 we focused attention on Neron models themselves, as opposed to their generic fibres, by replacing category $\mathcal{N}_K$ with category $\mathcal{N}$; see Section 4.1.

@@

We added Example 4.8, which provides tori whose Neron models have the component groups appearing in Example 2.10.

@@

Finally, we added Remark 4.1 on quasicharacter sheaves and the Langlands correspondence for $p$-adic tori. 

>>>>

We reorganised the Introduction to reflect the changes discussed below. 
This included making a subsection called {\it Relation to other work}, following a recommendation.

@@

We removed Berstein's suggestion from the Introduction, since at the moment we are not able to pursue it. 
We continue to thank him in the Acknowledgements, as we intend to return to this issue, elsewhere.

@@

We changed nomenclature so that the paper now discusses two notions: {\it character sheaves} and {\it quasicharacter sheaves}. Character sheaves are based on a familiar concept: they are local systems on a smooth group scheme $G$ over a finite field $k$, equipped with some additional structure, and they provide a geometrization of characters of $G(k)$.  Quasicharacter sheaves provide a geometrization of quasicharacters of $p$-adic tori $T(K)$; they are local systems equipped with some additional structure, on the Greenberg transform of a N\'eron model. 

@@

In Section 4 we focused attention on N\'eron models themselves, as opposed to their generic fibres, by replacing category $\mathcal{N}_K$ with category $\mathcal{N}$; see Section 4.1.

@@

We added Example 4.8, which provides tori whose N\'eron models have the component groups appearing in Example 2.10.

@@

Finally, we added Remark 4.10 on quasicharacter sheaves and the Langlands correspondence for $p$-adic tori. 
